---
title: Graph Gallery
---

👋 **Bizard** is a comprehensive repository of advanced visualization codes tailored for biomedical research. It currently includes approximately 750 graphics across more than 65 chart types. Below is the gallery for all graphics.

Each graph is a row in the table. You can click on the graph to zoom in for a preview. Clicking on the blue title of a graph will take you to the corresponding graphic tutorial page. The table's Search box provides graph search function.

## 🎯 Smart Graph Recommender

Describe your visualization goal, and we'll recommend the best matching charts:

<div id="recommender-widget" class="recommender-container">
  <textarea id="recommender-input" rows="3" placeholder="e.g., I want to compare gene expression between different cancer types..." style="width: 100%; padding: 8px; border: 1px solid #ccc; border-radius: 4px; font-family: inherit;"></textarea>
  <br>
  <button id="recommender-btn" onclick="recommendChartsEn()" style="margin-top: 8px; padding: 8px 16px; background: #007899; color: white; border: none; border-radius: 4px; cursor: pointer;">Recommend Charts</button>
  <div id="recommender-results" style="margin-top: 16px;"></div>
</div>

```{r}
#| echo: false
#| message: false
#| warning: false

library(reactable)
library(jsonlite)
library(dplyr)
library(crosstalk)
library(htmltools)

data <- read.csv("files/gallery_data.csv")
```

## 𝐁𝐀𝐒𝐈𝐂𝐒

### Distribution Gallery

```{r}
#| echo: false
data_Distribution <- data[data$Level2=="Distribution",]

tbl <- reactable(
  data_Distribution,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Correlation Gallery

```{r}
#| echo: false
data_Correlation <- data[data$Level2=="Correlation",]

tbl <- reactable(
  data_Correlation,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Ranking Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Ranking",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Composition/Part Of The Whole Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Composition",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Data Over Time/Evolution Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Evolution",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Proportion/Flow Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Proportion",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### Animation Gallery

```{r}
#| echo: false
data_Ranking <- data[data$Level2=="Animation",]

tbl <- reactable(
  data_Ranking,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

## 𝐎𝐌𝐈𝐂𝐒

```{r}
#| echo: false
data_OMICS <- data[data$Level1=="OMICS",]

tbl <- reactable(
  data_OMICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```


## 𝐂𝐋𝐈𝐍𝐈𝐂𝐒

```{r}
#| echo: false
data_OMICS <- data[data$Level1=="CLINICS",]

tbl <- reactable(
  data_OMICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

## 𝐏𝐘𝐓𝐇𝐎𝐍

```{r}
#| echo: false
data_PYTHON <- data[data$Level1=="PYTHON",]

tbl <- reactable(
  data_PYTHON,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

## 𝐉𝐔𝐋𝐈𝐀

```{r}
#| echo: false
data_JULIA <- data[data$Level1=="JULIA",]

tbl <- reactable(
  data_JULIA,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

## 𝐇𝐈𝐏𝐋𝐎𝐓

### BASICS

```{r}
#| echo: false
data_HIPLOT_BASICS <- data[data$Level1=="HIPLOT" & data$Level2=="BASICS",]

tbl <- reactable(
  data_HIPLOT_BASICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### OMICS

```{r}
#| echo: false
data_HIPLOT_OMICS <- data[data$Level1=="HIPLOT" & data$Level2=="OMICS",]

tbl <- reactable(
  data_HIPLOT_OMICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### CLINICS

```{r}
#| echo: false
data_HIPLOT_CLINICS <- data[data$Level1=="HIPLOT" & data$Level2=="CLINICS",]

tbl <- reactable(
  data_HIPLOT_CLINICS,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```

### MAP

```{r}
#| echo: false
data_HIPLOT_MAP <- data[data$Level1=="HIPLOT" & data$Level2=="MAP",]

tbl <- reactable(
  data_HIPLOT_MAP,
  defaultColDef = colDef(vAlign = "center", headerClass = "header"),
  columns = list(
    Id = colDef(
      name = "Id", align = "center", minWidth = 70, maxWidth = 90
    ),
    Name = colDef(
      name = "Graph", cell = JS("renderGraph"), html = TRUE, minWidth = 250
    ),
    Image_url = colDef(show = FALSE),
    Tutorial_url = colDef(show = FALSE),
    Description =colDef(show = FALSE),
    Type = colDef(name = "Type"),
    Level1 =colDef(show = FALSE),
    Level2 =colDef(show = FALSE)
  ), 
  searchable = TRUE,
  defaultPageSize = 7
)

div(
  class = "movies",
  tbl,
  div(id = "modal",  class="modal", onclick="hideModal()",
      img(
        id="modal-image", class="modal-image"
      ))
)
```






```{js, echo=FALSE}

function renderGraph(cellInfo) {
  const url = cellInfo.row['Tutorial_url']
  const imageSrc = cellInfo.row['Image_url']
  const altText = cellInfo.value
  const description = cellInfo.row['Description']
  const poster = `<img src="${imageSrc}" class="movie-poster" alt="${altText}" onclick="showModal(this)">`

  const title = `<a href="${url}" target="_blank">${cellInfo.value}</a>`

  const details = `<div class="movie-info-details">${description}</div>`
  const text = `<div class="movie-info-text">${title}${details}</div>`
  return `<div class="movie-info">${poster}${text}</div>`
}

function showModal(image) {
  var modal = document.getElementById("modal");
  var modalImage = document.getElementById("modal-image");
  modal.style.display = "block";
  modalImage.src = image.src;
}

function hideModal() {
  var modal = document.getElementById("modal");
  modal.style.display = "none";
}

// Smart Recommender Functions (English + Chinese bilingual support)
let keywordsDataEn = null;

// XSS sanitization helper
function sanitize(str) {
  if (!str) return '';
  const div = document.createElement('div');
  div.textContent = str;
  return div.innerHTML;
}

async function loadKeywordsEn() {
  if (!keywordsDataEn) {
    try {
      // Load both English and Chinese dictionaries for bilingual support
      const responseEn = await fetch('files/recommender_keywords.json');
      const responseZh = await fetch('files/recommender_keywords_zh.json');
      if (!responseEn.ok || !responseZh.ok) {
        throw new Error(`Failed to load keywords`);
      }
      const dataEn = await responseEn.json();
      const dataZh = await responseZh.json();

      // Merge both dictionaries
      keywordsDataEn = {
        synonyms: { ...dataEn.synonyms, ...dataZh.synonyms },
        intentKeywords: { ...dataEn.intentKeywords, ...dataZh.intentKeywords }
      };
    } catch (error) {
      console.error('Error loading keywords:', error);
      throw error;
    }
  }
  return keywordsDataEn;
}

function tokenize(text) {
  // Bilingual tokenization: handle both English words and Chinese characters
  const englishTokens = text.toLowerCase().split(/[\s,.!?;:'"()\[\]]+/).filter(t => t.length > 0 && !/[\u4e00-\u9fa5]/.test(t));
  const chineseTokens = text.match(/[\u4e00-\u9fa5]+/g) || [];
  return [...englishTokens, ...chineseTokens];
}

function extractKeywords(text, synonyms) {
  // Scan the text for all known keywords (handles Chinese without tokenization)
  const found = new Set();
  const textLower = text.toLowerCase();

  // Check all synonym keys and their values
  Object.keys(synonyms).forEach(key => {
    // Check if key appears in text
    if (text.includes(key) || textLower.includes(key.toLowerCase())) {
      found.add(key);
      synonyms[key].forEach(syn => found.add(syn));
    }
    // Check if any synonym value appears in text
    synonyms[key].forEach(syn => {
      if (text.includes(syn) || textLower.includes(syn.toLowerCase())) {
        found.add(syn);
        found.add(key);
        synonyms[key].forEach(s => found.add(s));
      }
    });
  });

  // Also add English tokens for mixed input
  const tokens = tokenize(text);
  tokens.forEach(t => found.add(t));

  return Array.from(found);
}

function expandSynonyms(tokens, synonyms) {
  const expanded = new Set(tokens);
  tokens.forEach(token => {
    const tokenLower = token.toLowerCase();
    const isChinese = /[\u4e00-\u9fa5]/.test(token);

    // Check if token is a synonym key (handle both English and Chinese)
    if (synonyms[token] || synonyms[tokenLower]) {
      const syns = synonyms[token] || synonyms[tokenLower];
      syns.forEach(syn => {
        expanded.add(syn);
        if (!/[\u4e00-\u9fa5]/.test(syn)) expanded.add(syn.toLowerCase());
      });
    }
    // Check if any synonym values contain the token
    Object.keys(synonyms).forEach(key => {
      const synValues = synonyms[key];
      if (synValues.includes(token) || synValues.includes(tokenLower) || key === token || key === tokenLower) {
        expanded.add(key);
        synValues.forEach(syn => {
          expanded.add(syn);
          if (!/[\u4e00-\u9fa5]/.test(syn)) expanded.add(syn.toLowerCase());
        });
      }
    });
  });
  return Array.from(expanded);
}

function matchIntents(tokens, intentKeywords) {
  const matched = [];
  Object.keys(intentKeywords).forEach(intent => {
    const keywords = intentKeywords[intent];
    if (keywords.some(kw => tokens.includes(kw.toLowerCase()))) {
      matched.push(intent);
    }
  });
  return matched;
}

function calculateScore(tokens, intents, text, chart) {
  let score = 0;

  // Base keyword match (handle both Chinese and English)
  tokens.forEach(token => {
    if (text.includes(token) || text.toLowerCase().includes(token.toLowerCase())) score += 1;
  });

  // Intent match bonus (each matched intent adds points)
  intents.forEach(intent => {
    score += 2;
  });

  // Type exact match bonus
  if (tokens.some(t => chart.Type.includes(t) || chart.Type.toLowerCase().includes(t.toLowerCase()))) score += 3;

  return score;
}

async function recommendChartsEn() {
  const input = document.getElementById('recommender-input').value.trim();
  const resultsDiv = document.getElementById('recommender-results');
  const btn = document.getElementById('recommender-btn');

  if (!input) {
    resultsDiv.innerHTML = '<p style="color: #666;">Please enter a description of your visualization goal.</p>';
    return;
  }

  // Show loading state
  const originalBtnText = btn.textContent;
  btn.disabled = true;
  btn.textContent = 'Searching...';
  resultsDiv.innerHTML = '<p style="color: #666;">Searching for matching charts...</p>';

  try {
    // Load keywords
    const keywords = await loadKeywordsEn();

    // Get chart data from existing CSV (already loaded in R chunk)
    // We need to fetch the CSV again for JS access
    const csvResponse = await fetch('files/gallery_data.csv');
    if (!csvResponse.ok) {
      throw new Error(`Failed to load chart data: ${csvResponse.status}`);
    }
    const csvText = await csvResponse.text();
    const chartData = parseCSV(csvText);

    // Extract keywords from input using new scanning method
    const extractedKeywords = extractKeywords(input, keywords.synonyms);
    const expandedTokens = expandSynonyms(extractedKeywords, keywords.synonyms);
    const matchedIntents = matchIntents(expandedTokens, keywords.intentKeywords);

    // Score each chart
    const results = chartData.map(chart => {
      const searchableText = `${chart.Name} ${chart.Description} ${chart.Type} ${chart.Level1} ${chart.Level2}`;
      const score = calculateScore(expandedTokens, matchedIntents, searchableText, chart);
      return { chart, score, matchedKeywords: expandedTokens.filter(t => searchableText.includes(t) || searchableText.toLowerCase().includes(t.toLowerCase())) };
    }).filter(r => r.score > 0)
      .sort((a, b) => b.score - a.score)
      .slice(0, 5);

    // Display results
    if (results.length === 0) {
      resultsDiv.innerHTML = '<p style="color: #666;">No matching charts found. Try different keywords.</p>';
      return;
    }

    resultsDiv.innerHTML = `<p style="font-weight: 600;">Matching Results (${results.length}):</p>` +
      results.map(r => `
        <div class="recommender-card" style="display: flex; align-items: center; margin: 8px 0; padding: 12px; border: 1px solid #e0e0e0; border-radius: 4px; background: #fafafa;">
          <img src="${sanitize(r.chart.Image_url)}" style="width: 80px; height: 80px; object-fit: cover; border-radius: 4px; margin-right: 12px;" onclick="showModal(this)">
          <div style="flex: 1;">
            <a href="${sanitize(r.chart.Tutorial_url)}" target="_blank" style="color: #007899; font-weight: 600; text-decoration: none;">${sanitize(r.chart.Name)}</a>
            <p style="margin: 4px 0 0 0; color: #666; font-size: 0.9em;">${sanitize(r.chart.Description)}</p>
            <p style="margin: 4px 0 0 0; color: #888; font-size: 0.8em;">Matched: ${r.matchedKeywords.slice(0, 5).map(k => sanitize(k)).join(', ')}</p>
          </div>
        </div>
      `).join('');
  } catch (error) {
    console.error('Error in chart recommendation:', error);
    resultsDiv.innerHTML = '<p style="color: #c00;">An error occurred while searching. Please try again.</p>';
  } finally {
    // Restore button state
    btn.disabled = false;
    btn.textContent = originalBtnText;
  }
}

function parseCSV(text) {
  const lines = text.trim().split('\n');
  const headers = lines[0].split(',');
  return lines.slice(1).map(line => {
    const values = line.split(',');
    const obj = {};
    headers.forEach((h, i) => obj[h] = values[i] || '');
    return obj;
  });
}
```

```{css, echo=FALSE}

/* Font from https://fontsarena.com/hanken-grotesk-by-hanken-design-co/ */
@font-face {
  font-family: 'Hanken Grotesk';
  font-style: normal;
  font-weight: 400;
  src: url("fonts/HKGrotesk-Regular.woff2") format("woff2"),
       url("fonts/HKGrotesk-Regular.woff") format("woff");
}

@font-face {
  font-family: 'Hanken Grotesk';
  font-style: normal;
  font-weight: 600;
  src: url("fonts/HKGrotesk-SemiBold.woff2") format("woff2"),
       url("fonts/HKGrotesk-SemiBold.woff") format("woff");
}

@font-face {
  font-family: 'Hanken Grotesk';
  font-style: normal;
  font-weight: 700;
  src: url("fonts/HKGrotesk-Bold.woff2") format("woff2"),
       url("fonts/HKGrotesk-Bold.woff") format("woff");
}

.movies {
  font-family: 'Hanken Grotesk', Helvetica, Arial, sans-serif;
}

.movies h2 {
  font-weight: 600;
}

.movies a {
  color: #007899;
  text-decoration: none;
}

.movies a:hover,
.movies a:focus {
  text-decoration: underline;
  text-decoration-thickness: max(1px, 0.0625rem);
}

.movies-tbl {
  margin-top: 1rem;
  font-size: 1rem;
}

.header {
  color: hsl(0, 0%, 45%);
  font-weight: 700;
  font-size: 0.8125rem;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}

.header:hover[aria-sort],
.header[aria-sort='ascending'],
.header[aria-sort='descending'] {
  color: hsl(0, 0%, 5%);
}

.movie-info {
  display: flex;
  align-items: center;
}

.movie-info-text {
  margin-left: 0.75rem;
  font-weight: 600;
  overflow: hidden;
  text-overflow: ellipsis;
}

.movie-info-details {
  margin-top: 0.125rem;
  font-size: 0.875rem;
  font-weight: 400;
  color: hsl(0, 0%, 40%);
  overflow: hidden;
  text-overflow: ellipsis;
}

.movie-poster {
  width: 100px;
  height: 100px;
  box-shadow: 0 0 0 1px hsl(0, 0%, 95%);
  cursor: zoom-in;
}

.movie-runtime {
  display: inline-block;
}

.movie-rating {
  margin-right: 0.25rem;
  padding: 0 0.25rem;
  border: 1px solid hsl(0, 0%, 75%);
  border-radius: 2px;
}

.user-score {
  font-weight: 600;
}

.filters {
  display: flex;
  flex-wrap: wrap;
  margin-top: 1rem;
  margin-left: -32px;
}

.filter-input {
  margin-top: 0.5rem;
  margin-left: 32px;
  flex: 1;
  min-width: 250px;
}

.filter-input label {
  color: hsl(0, 0%, 45%);
  font-weight: 700;
  font-size: 0.8125rem;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}

.filter-input select,
.filter-input input[type="search"] {
  padding: 0 0.375rem;
  height: 2rem;
}

.filter-input input[type="search"] {
  /* Revert Bootstrap 5's Reboot styles, which change native search input styling */
  -webkit-appearance: searchfield;
  outline-offset: revert;
  border-color: revert;
}


.modal {
  display: none;
  position: fixed;
  z-index: 9999;
  top: 0;
  left: 0;
  width: 100%;
  height: 100%;
  background-color: rgba(0, 0, 0, 0.8);
  cursor: zoom-out;
}

.modal-image {
  display: block;
  max-width: 90%;
  max-height: 90%;
  margin: auto;
  margin-top: 5%;
}

/* Smart Recommender Styles */
.recommender-container {
  margin: 1.5rem 0;
  padding: 1rem;
  border: 1px solid #e0e0e0;
  border-radius: 8px;
  background: #f9f9f9;
}

.recommender-card:hover {
  background: #f0f0f0;
  border-color: #007899;
}
```
