---
title: "Barplot Color Group"
author:
  - "**[Editor]** Hu Zheng;"
  - "**[Contributors]** "
---

The color group barplot can be used to display data values in groups, and to label different colors in sequence.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `ggplot2`; `stringr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("stringr", quietly = TRUE)) {
  install.packages("stringr")
}

# Load packages
library(ggplot2)
library(stringr)
```

## Data Preparation

Data table (three columns):

Term | Entry name, such as GO/KEGG channel name

Count | The numerical size of the entry, such as the number of genes enriched in a pathway

Type | Category to which this channel belongs: such as BP/MF/CC/KEGG

```{r load data, message=FALSE}
# Load data
data <- read.delim("files/Hiplot/004-barplot-color-group-data.txt", header = T)

# convert data structure
colnames(data) <- c("term", "count", "type")
data[,"term"] <- str_to_sentence(str_remove(data[,"term"], pattern = "\\w+:\\d+\\W"))
data[,"term"] <- factor(data[,"term"], 
                        levels =  data[,"term"][length(data[,"term"]):1])
data[,"type"] <- factor(data[,"type"], 
                        levels = data[!duplicated(data[,"type"]), "type"])

# View data
data
```

## Visualization

```{r fig-1barplot-color-group}
#| label: fig-1barplot-color-group
#| fig-cap: "Barplot Color Group"
#| out.width: "95%"
#| warning: false

# Barplot Color Group
p <- ggplot(data = data, aes(x = term, y = count, fill = type)) +
  geom_bar(stat = "identity", width = 0.8) + 
  theme_bw() +
  xlab("Count") +
  ylab("Term") +
  guides(fill = guide_legend(title="Type")) +
  ggtitle("Barplot Color Group") + 
  coord_flip() +
  theme_classic() +
  scale_fill_manual(values = c("#E64B35FF","#4DBBD5FF","#00A087FF","#3C5488FF")) +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

This plot visualizes the results of GO/KEGG pathway enrichment analysis.

