---
title: "Beeswarm"
author:
  - "**[Editor]** Hu Zheng;"
  - "**[Contributors]** "
---

The beeswarm is a noninterference scatter plot which is similar to a bee colony.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `ggbeeswarm`; `ggthemes`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("ggbeeswarm", quietly = TRUE)) {
  install.packages("ggbeeswarm")
}
if (!requireNamespace("ggthemes", quietly = TRUE)) {
  install.packages("ggthemes")
}

# Load packages
library(ggbeeswarm)
library(ggthemes)
```

## Data Preparation

The loaded data are different groups and their data.

```{r load data, message=FALSE}
# Load data
data <- read.table("files/Hiplot/012-beeswarm-data.txt", header = T)

# convert data structure
data[, 1] <- factor(data[, 1], levels = unique(data[, 1]))
colnames(data) <- c("Group", "y")

# View data
head(data)
```

## Visualization

```{r fig-1Beeswarm}
#| label: fig-1Beeswarm
#| fig-cap: "Beeswarm"
#| out.width: "95%"
#| warning: false

# Beeswarm
p <- ggplot(data, aes(Group, y, color = Group)) +
  geom_beeswarm(alpha = 1, size = 0.8) +
  labs(x = NULL, y = "value") +
  ggtitle("BeeSwarm Plot") +
  scale_color_manual(values = c("#e04d39","#5bbad6","#1e9f86")) +
  theme_stata() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

Different colors represent different groups, and dots represent data.


