---
title: "Calibration Curve"
author:
  - "**[Editor]** Hu Zheng;"
  - "**[Contributors]** "
---

The calibration curve is used to evaluate the consistency / calibration, i.e. the difference between the predicted value and the real value.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `survival`; `rms`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("survival", quietly = TRUE)) {
  install.packages("survival")
}
if (!requireNamespace("rms", quietly = TRUE)) {
  install.packages("rms")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(survival)
library(rms)
library(ggplotify)
```

## Data Preparation

Data frame of multi columns data (Numeric allow NA). i.e the survival data (status with 0 and 1).

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.table("files/Hiplot/018-calibration-curve-data.txt", header = T)

# convert data structure
res.lrm <- lrm(as.formula(paste(
  "status ~ ", 
  paste(colnames(data)[3:length(colnames(data))], collapse = "+"))),
  data = data, x = TRUE, y = TRUE)

lrm.cal <- calibrate(res.lrm, method = "boot", B = length(rownames(data)))

# View data
head(data)
```

## Visualization

```{r fig-1Calibration-curve}
#| label: fig-1Calibration-curve
#| fig-cap: "Calibration Curve"
#| out.width: "95%"
#| warning: false
#| message: false

# Calibration Curve
p <- as.ggplot(function() {
  plot(lrm.cal,
       xlab = "Nomogram Predicted Survival",
       ylab = "Actual Survival",
       main = "Calibration Curve"
       )
})

p
```

