---
title: "Dotchart"
author:
  - "**[Editor]** Hu Zheng;"
  - "**[Contributors]** "
---

Sliding bead chart is a graph of beads sliding on a column. It is the superposition of bar chart and scatter chart.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `ggpubr`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("ggpubr", quietly = TRUE)) {
  install.packages("ggpubr")
}

# Load packages
library(ggpubr)
```

## Data Preparation

The loaded data are gene names and their corresponding gene expression values and groups.

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/046-dotchart-data.txt", header = T)

# View data
head(data)
```

## Visualization

```{r fig-1Dotchart}
#| label: fig-1Dotchart
#| fig-cap: "Dotchart"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 8
#| warning: false
#| message: false

# Dotchart
p <- ggdotchart(data, x = "Name", y = "Value", group = "Group", color = "Group",
                rotate = T, sorting = "descending",
                y.text.col = F, add = "segments", dot.size = 2) +
  xlab("Name") +
  ylab("Value") +
  ggtitle("DotChart Plot") +
  scale_color_manual(values = c("#e04d39","#5bbad6","#1e9f86")) +
  theme_classic() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

Each color represents a different grouping, so that the differences in gene expression values can be intuitively understood.
