---
title: "Fishplot"
author:
  - "**[Editor]** Hu Zheng;"
  - "**[Contributors]** "
---

Clone evolution analysis

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `fishplot`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("fishplot", quietly = TRUE)) {
  install_github("chrisamiller/fishplot")
}

# Load packages
library(fishplot)
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/055-fishplot-data.txt", header = T)

# View data
head(data)
```

- **timepoints**: specifying the timepoints for each column of the matrix

- **parents**: specifying parental relationships between clones

- **samplename**: samplename (support multiple samples)

- **other**: a numeric matrix containing tumor fraction estimates for all clones at all timepoints

## Visualization

```{r fig-1Fan}
#| label: fig-1Fan
#| fig-cap: "Fishplot"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 10
#| warning: false
#| message: false

## Create a fish object
fish = createFishObject(as.matrix(data[,4:7]), parents=data$parents, 
                        timepoints=data$timepoints, 
                        col = c("#888888","#e8130c","#f8150d","#55158f"))
## Calculate the layout of the drawing
fish = layoutClones(fish)
## Draw the plot, using the splining method (recommended), and providing both timepoints to label and a plot title
fishPlot(fish,shape="spline", title.btm="Sample1", title = "Fishplot",
         cex.title=1, vlines=c(0,30,75,150), 
         vlab=c("Day 0","Day 30","Day 75","Day 150"))
```

