---
title: "Histogram"
author:
  - "**[Editor]** Hu Zheng;"
  - "**[Contributors]** "
---

Histogram refers to the distribution of continuous variable data by a series of vertical stripes or line segments with different heights.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `ggplot2`; `ggthemes`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
if (!requireNamespace("ggthemes", quietly = TRUE)) {
  install.packages("ggthemes")
}

# Load packages
library(ggplot2)
library(ggthemes)
```

## Data Preparation

The loaded data is the data set (data on treatment outcomes of different treatment regimens).

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/088-histogram-data.txt", header = T)

# Convert data structure
data[, 2] <- factor(data[, 2], levels = unique(data[, 2]))

# View data
head(data)
```

## Visualization

```{r fig-1histogram}
#| label: fig-1histogram
#| fig-cap: "Histogram"
#| out.width: "95%"
#| fig-height: 7
#| fig-width: 10
#| warning: false
#| error: false
#| message: false

# Histogram
p <- ggplot(data, aes(x=Value, fill=Group2)) +
  geom_histogram(alpha = 1, bins = 12, col = "white") +
  ggtitle("Histogram Plot") +
  scale_fill_manual(values = c("#e04d39","#5bbad6","#1e9f86")) +
  theme_stata() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

The width of the rectangle in the figure is proportional to and different from the spacing, and the vertical axis represents the frequency.

