---
title: "Meta-analysis of Binary Data"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---


::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Meta-analysis of Binary Data` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/meta-bin?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `meta`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("meta", quietly = TRUE)) {
  install.packages("meta")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(meta)
library(ggplotify)
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/119-meta-bin-data.txt", header = T)

# Convert data structure
m1 <- metabin(ev.exp, n.exp, ev.cont, n.cont, studlab = Study, data = data)

# View data
head(data)
```

## Visualization

```{r fig-1meta-bin}
#| label: fig-1meta-bin
#| fig-cap: "Meta-analysis of Binary Data"
#| out.width: "95%"
#| fig-height: 7
#| fig-width: 12
#| warning: false
#| error: false
#| message: false

# Meta-analysis of Binary Data
p <- as.ggplot(function(){
  meta::forest(m1, layout = "meta")
  })

p
```


