---
title: "Mosaic Ratio Plot"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Mosaic Ratio Plot` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/mosaic?lang=en>
:::

Use mosaic blocks to show data proportions.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `vcd`; `DescTools`; `ggplotify`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("vcd", quietly = TRUE)) {
  install.packages("vcd")
}
if (!requireNamespace("DescTools", quietly = TRUE)) {
  install.packages("DescTools")
}
if (!requireNamespace("ggplotify", quietly = TRUE)) {
  install.packages("ggplotify")
}

# Load packages
library(vcd)
library(DescTools)
library(ggplotify)
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/123-mosaic-data.txt", header = T)

# Convert data structure
tbl <- xtabs(~ Survived + PassengerClass + Gender, data)

# View data
head(data)
```

## Visualization

```{r fig-1mosaic}
#| label: fig-1mosaic
#| fig-cap: "Mosaic Ratio Plot"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Mosaic Ratio Plot
p <- as.ggplot(function() {
  mosaic(tbl, shade = TRUE, legend = TRUE, main = "Mosaic Ratio Plot",
         gp = shading_binary(tbl, col = c("#3B4992FF","#EE0000FF")))
})

p
```


