---
title: "Multiple Histograms"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Multiple Histograms` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/multiple-histograms?lang=en>
:::

Multiple histograms are plotted on the same graph to compare differences between multiple sets of data.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

# Load packages
library(ggplot2)
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/125-multiple-histograms-data.txt", header = T)

# View data
head(data)
```

## Visualization

```{r fig-1multiple-histograms}
#| label: fig-1multiple-histograms
#| fig-cap: "Multiple Histograms"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# Multiple Histograms
p <- ggplot(data, aes(x = value, fill = type)) +
  geom_histogram(color = "black", alpha = 0.5, 
                 position = "identity", binwidth = 0.3) +
  scale_fill_manual(values = c("#BC3C29FF","#0072B5FF")) +
  theme_bw()

p
```


