---
title: "Parallel Coordinate"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `Parallel Coordinate` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/parallel-coordinate?lang=en>
:::

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `GGally`; `hrbrthemes`; `viridis`; `ggthemes`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("GGally", quietly = TRUE)) {
  install.packages("GGally")
}
if (!requireNamespace("hrbrthemes", quietly = TRUE)) {
  install.packages("hrbrthemes")
}
if (!requireNamespace("viridis", quietly = TRUE)) {
  install.packages("viridis")
}
if (!requireNamespace("ggthemes", quietly = TRUE)) {
  install.packages("ggthemes")
}

# Load packages
library(GGally)
library(hrbrthemes)
library(viridis)
library(ggthemes)
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/132-parallel-coordinate-data.txt", header = T)

# Convert data structure
data[, 6] <- factor(data[, 6], levels = unique(data[, 6]))

# View data
head(data)
```

## Visualization

```{r fig-1parallel-coordinate}
#| label: fig-1parallel-coordinate
#| fig-cap: "Parallel Coordinate"
#| out.width: "95%"
#| fig-height: 4
#| fig-width: 10
#| warning: false
#| error: false
#| message: false

# Parallel Coordinate
p <- ggparcoord(data, columns = 2:(ncol(data) - 1), groupColumn = ncol(data),
                title = "Parallel Coordinate Plot for cancer Data",
                alphaLines = 0.3, scale = "globalminmax",
                showPoints = T, boxplot = F) +
  theme_base() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12, hjust = 0.5),
        axis.title = element_text(size = 10),
        axis.text = element_text(size = 12),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) +
  scale_color_viridis(discrete = TRUE) +
  facet_grid(formula(paste("~", (colnames(data)[ncol(data)]))))

p
```


