---
title: "PCA2"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `PCA2` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/pca2?lang=en>
:::

Principal component analysis (PCA) is a data processing method with "dimension reduction" as the core, replacing multi-index data with a few comprehensive indicators (PCA), and restoring the most essential characteristics of data.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `FactoMineR`; `factoextra`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("FactoMineR", quietly = TRUE)) {
  install.packages("FactoMineR")
}
if (!requireNamespace("factoextra", quietly = TRUE)) {
  install.packages("factoextra")
}

# Load packages
library(FactoMineR)
library(factoextra)
```

## Data Preparation

The loaded data are set (gene name and corresponding gene expression value) and sample information (sample name and grouping).

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/135-pca2-data1.txt", header = T)
sample_info <- read.delim("files/Hiplot/135-pca2-data2.txt", header = T)

# Convert data structure
row.names(sample_info) <- sample_info[,1]
sample_info <- sample_info[colnames(data)[-1],]
## tsne
rownames(data) <- data[, 1]
data <- as.matrix(data[, -1])
pca_data <- PCA(t(as.matrix(data)), scale.unit = TRUE, ncp = 5, graph = FALSE)

# View data
head(data)
```

## Visualization

```{r fig-1pca2}
#| label: fig-1pca2
#| fig-cap: "PCA2"
#| out.width: "95%"
#| fig-height: 5
#| fig-width: 6
#| warning: false
#| error: false
#| message: false

# PCA2
p <- fviz_pca_ind(pca_data, geom.ind = "point", pointsize = 6, addEllipses = TRUE,
                  mean.point = F, col.ind = sample_info[,"Group"]) +
  ggtitle("Principal Component Analysis") +
  scale_fill_manual(values = c("#00468BFF","#ED0000FF")) +
  scale_color_manual(values = c("#00468BFF","#ED0000FF")) +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```

Different colors represent different samples, which can explain the relationship between principal components and original variables. For example, M1 has a greater contribution to PC1, while M8 has a greater negative correlation with PC1.


