---
title: "EnhancedMA"
author:
  - "**[Editor]** [Hu Zheng](https://github.com/ZhengTiger);"
  - "**[Contributors]** "
---

::: callout-note
**Hiplot website**

This page is the tutorial for source code version of the Hiplot `EnhancedMA` plugin. You can also use the Hiplot website to achieve no code ploting. For more information please see the following link:

<https://hiplot.cn/basic/pseudo-enhanced-ma?lang=en>
:::

Visualization of differentially expressed genes.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `EnhancedVolcano`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("EnhancedVolcano", quietly = TRUE)) {
  install_github('kevinblighe/EnhancedVolcano')
}

# Load packages
library(EnhancedVolcano)
```

## Data Preparation

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.delim("files/Hiplot/143-pseudo-enhanced-ma-data.txt", header = T)

# Convert data structure
row.names(data) <- data[,1]
data <- data[,-1]
data$baseMeanNew <- 1 / (10^log(data$baseMean + 1))

# View data
head(data)
```

## Visualization

```{r fig-1pseudo-enhanced-ma}
#| label: fig-1pseudo-enhanced-ma
#| fig-cap: "EnhancedMA"
#| out.width: "95%"
#| fig-height: 8
#| fig-width: 8
#| warning: false
#| error: false
#| message: false

# EnhancedMA
p <- EnhancedVolcano(
  data, lab = rownames(data), title = "MA plot", subtitle = "EnhancedMA",
  x = 'log2FoldChange', y = 'baseMeanNew', xlab = bquote(~Log[2]~ 'fold change'),
  ylab = bquote(~Log[e]~ 'base mean + 1'), ylim = c(0,12),
  pCutoff = as.numeric(1e-05), FCcutoff = 1, pointSize = 3.5,
  labSize = 4, boxedLabels = T, colAlpha = 1,
  legendLabels = c('NS', expression(Log[2]~FC),
                   'Mean expression', 
                   expression(Mean-expression~and~log[2]~FC)),
  legendPosition = "bottom", legendLabSize = 16, legendIconSize = 4.0,
  encircleCol = 'black', encircleSize = 2.5, encircleFill = 'pink',
  encircleAlpha = 1/2) + 
  coord_flip() +
  theme(text = element_text(family = "Arial"),
        plot.title = element_text(size = 12,hjust = 0.5),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 0, hjust = 0.5,vjust = 1),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

p
```



