---
title: "PCA Analysis"
author:
  - "**[Editor]** Yi Xuyang;"
- "**[Contributors]** "
---
  
## Setup
  
-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming language: R

-   Dependent packages: `gmodels`, `ggpubr`, `openxlsx`, `ggplot2`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install and load packages
if (!requireNamespace("gmodels", quietly = TRUE)) {
  install.packages("gmodels")
}
if (!requireNamespace("ggpubr", quietly = TRUE)) {
  install.packages("ggpubr")
}
if (!requireNamespace("openxlsx", quietly = TRUE)) {
  install.packages("openxlsx")
}
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
# Load packages
library(gmodels)
library(ggpubr)
library(openxlsx)
library(ggplot2)

## Data Preparation

The loaded data are set (gene name and corresponding gene expression value) and sample information (sample name and grouping).

```{r load data, message=FALSE, warning=FALSE}
# Load data
data <- read.table("187-pca-data.txt", header = T,sep = ",")
group <- read.table("187-pca-group.txt", header = T,sep = ",")

rownames(data) <- data[, 1]
data <- as.matrix(data[, -1])

# Create configuration
conf <- list(
  dataArg = list(
    list(list(value = "group")),  # Color by group column
    list(list(value = ""))         # No shape grouping
  ),
  general = list(
    title = "Principal Component Analysis",
    palette = "Set1"
  )
)

# Perform PCA - Note: data must be transposed because PCA analyzes samples (columns)
pca_info <- prcomp(t(data), scale. = TRUE)

# Prepare plot data
axis <- sapply(conf$dataArg[[1]], function(x) x$value)

# Process color grouping
if (is.null(axis[1]) || axis[1] == "") {
  colorBy <- rep('ALL', ncol(data))
} else {
  # Ensure sample order matches
  colorBy <- group[match(colnames(data), group$sample), axis[1]]
}
colorBy <- factor(colorBy, levels = unique(colorBy))

# Create PCA data frame
pca_data <- data.frame(
  sample = rownames(pca_info$x),
  PC1 = pca_info$x[, 1],
  PC2 = pca_info$x[, 2],
  colorBy = colorBy
)

# Calculate explained variance
variance_explained <- round(pca_info$sdev^2 / sum(pca_info$sdev^2) * 100, 1)

# View prepared data
str(data)
str(group)
head(pca_data)
```

## Visualization

```{r fig-1interval-bar-chart}
#| label: fig-pca
#| fig-cap: "PCA Analysis"
#| out.width: "95%"
#| fig-height: 6
#| fig-width: 8

# Create PCA plot
p <- ggplot(pca_data, aes(x = PC1, y = PC2, color = colorBy)) +
  geom_point(size = 4, alpha = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray70") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray70") +
  stat_ellipse(level = 0.95, show.legend = FALSE) +
  ggtitle(conf$general$title) +
  labs(
    x = paste0("PC1 (", variance_explained[1], "%)"),
    y = paste0("PC2 (", variance_explained[2], "%)"),
    color = axis[1]
  ) +
  
  # Custom color scheme
  scale_color_brewer(palette = conf$general$palette) +
  
  # Add sample labels
  geom_text(aes(label = sample), 
            hjust = 0.5, vjust = -1, size = 3.5, show.legend = FALSE) +
  
  # Theme settings
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    axis.title = element_text(size = 14, face = "bold"),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 11),
    legend.position = "right",
    panel.grid.major = element_line(color = "grey90", linewidth = 0.3),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(fill = NA, color = "grey50", linewidth = 0.5),
    aspect.ratio = 1
  )

# Display plot
p

```
