---
title: "Calend Highlight"
author:
  - "**[Editor]** [Benben Miao](https://github.com/benben-miao);"
---

Date highlighting marks are mainly used to display changes in data within certain specific date ranges in time series data, and can be used for an overview of activity frequencies and marking of special dates.

## Setup

-   System Requirements: Cross-platform (Linux/MacOS/Windows)

-   Programming Language: R

-   Dependencies: `calendR`

```{r packages setup, message=FALSE, warning=FALSE, output=FALSE}
# Install packages
if (!requireNamespace("calendR", quietly = TRUE)) {
  install.packages("calendR")
}

# Load packages
library(calendR)
```

## Data Preparation

The data is the calendar data for a specified year, and certain date ranges can be selected to be highlighted.

```{r load data}
# Construct data
set.seed(1)
data <- rnorm(365)

# View data
head(data)
```

## Visualization

### 1. Chinese Calendar

It should be noted that if you are in China, the default `weeknames` and `monthnames` are in Chinese; if you are in other countries/regions, the default `weeknames` and `monthnames` are in English.

```{r fig1CalendChina}
#| label: fig1CalendChina
#| fig-cap: "Chinese Calendar"
#| out.width: "95%"
#| warning: false

# Chinese Calendar
p <- calendR(
  year = 2025,
  month = NULL,
  from = NULL,
  to = NULL,
  start = "M",
  orientation = "portrait",
  special.days = data,
  special.col = "#FF0000",
  gradient = TRUE,
  low.col = "#FFFFFF",
  font.family = "sans",
  font.style = "plain",
  day.size = 3,
  weeknames = c("一", "二", "三", "四", "五", "六", "日"),
  monthnames = c(
    "一月",
    "二月",
    "三月",
    "四月",
    "五月",
    "六月",
    "七月",
    "八月",
    "九月",
    "十月",
    "十一月",
    "十二月"
  ),
  # ncol = 2,
  lunar = FALSE,
  pdf = FALSE
)

p
```

### 2. English Calendar

```{r fig1Calend}
#| label: fig1Calend
#| fig-cap: "English Calendar"
#| out.width: "95%"
#| warning: false

# English Calendar
p <- calendR(
  year = 2025,
  month = NULL,
  from = NULL,
  to = NULL,
  start = "S",
  orientation = "portrait",
  special.days = data,
  special.col = "#008888",
  gradient = TRUE,
  low.col = "#FFFFFF",
  font.family = "sans",
  font.style = "plain",
  day.size = 3,
  weeknames = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"),
  monthnames = c(
    "January",
    "February",
    "March",
    "April",
    "May",
    "June",
    "July",
    "August",
    "September",
    "October",
    "November",
    "December"
  ),
  # ncol = 2,
  lunar = FALSE,
  pdf = FALSE
)

p
```

### 3. Calendar Period

```{r fig1CalendPeriod}
#| label: fig1CalendPeriod
#| fig-cap: "Calendar Period"
#| out.width: "95%"
#| warning: false

# Calendar Period
data <- rnorm(30, 15, 10)
days <- rep(min(data) - 0.05, 365)
days[30:180] <- data

p <- calendR(
  year = 2021,
  month = NULL,
  start = "S",
  orientation = "portrait",
  special.days = days,
  low.col = "white",
  special.col = "#FF0000",
  weeknames = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"),
  monthnames = c(
    "January",
    "February",
    "March",
    "April",
    "May",
    "June",
    "July",
    "August",
    "September",
    "October",
    "November",
    "December"
  ),
  gradient = TRUE,
  legend.pos = "bottom"
)

p
```